---
title: "Mind Map: Text Extraction in Python, R, and Julia"
author: "Stefan Wojcik and Adam Hughes"
date: "`r format(Sys.Date())`"
output: 
  ioslides_presentation:
      logo: imgs/Twitter_Logo_Blue.png
  css: "newstyle.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning =  FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = TRUE)

library(readr)
library(ggplot2)
library(dplyr)
library(knitr)
library(srvyr)
```

## Identifying Political News

- Our goal: extract one important topic of interest in a corpus of text

### Challenges
- How to accurately classify political news without human coders?

- How to validate the accuracy of the classifier without ground truth?


## Methodology: Isolating Political News

1. A set of ‘seed’ words that we know are about the topic. 
2. Apply positive label to any documents containing those words and coming from known sources
3. Run a machine learning model to uncover the patterns of words corresponding to the positive examples
4. Extrapolate the model to the entire dataset to label everything

## Example: A Mind Map
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("imgs/mind_map.png"), 
               width = 600)
```


## URLS/Tweets Data

- Limit analysis to the last 21 days
- 837,932 links to known misinfo domains (in EN)
- 894,938 links to any site (random tweets in EN containing a URL)


## Methodology: Validation
```{r, echo=F}
recall = data_frame(Fragment = c("politi", "usnews", "world", "national", 
                             "state", "elect", "vote", "govern", "campaign", 
                             "war", "polic", "econ", "unemploy", "racis", 
                             "energy", "abortion", "educa", "healthcare", "immigration"), 
                Recall = c(.96, .45, .79, .85, .84, .85, .95, .98, 
                           .95, .98, .96, .88, .94, .95, .86, .98, .82, 
                           .84, .97), 
                Base_rate = c(.01, .0, .01, .01, .01, .01, .01, 0.0, 0.0, 0.0, 0.0, 
                              .01, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0))
recall$Fragment = factor(recall$Fragment, levels = recall$Fragment[order(recall$Recall)])
qplot(data=recall, y=Fragment, x=Recall)
```
- Results: >95% accurate on test set

## Results: Political shares by type of link
**About 20%** of random URLs are about politics
**About 80%** of misinformation URLS were about politics

## Results: Political misinfo over time
**Over time patterns of political misinfo tend to match trends of politics**
```{r, echo=F}
htmltools::img(src = knitr::image_uri("imgs/misinfo_over_time.png"), 
               width = 600)
```


## THANK YOU!
